Boosted

### 2016-12-13 SS/Regression.rmd
reset

library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library('caret')
library('pwr')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')

@@

```{r echo=FALSE}
some <- all7d %>% select(return.pdol, mlsto, inv.mlsto, timespan,no.users,Discipline,pc.pro,
                         client.totinv,code.director,Num.disc,Business,Biz.type,
                         code.contact,code.client,Project.Value,JD.Second,Post.Code,code.ProjEng,Billing.Type,
                         majority.pos,
                         pc.majpos)

@@

RMSE(ans$answer, ans$full.lm.fit)

@@

RMSE is 0.4768 which isn't great in terms of predicting return per dollar.
R^2 is 0.1905

Let's try deleting some full variables

```{r, echo=FALSE}
full.2<- update(full, .~. -client.totinv.log)
summary(full.2)
full.3<- update(full.2, .~. -code.director)
summary(full.3)
full.4<- update(full.3, .~. -Num.disc)
summary(full.4)
full.5<- update(full.4, .~. -code.ProjEng)
summary(full.5)
full.6<- update(full.5, .~. -Biz.type + Discipline)
summary(full.6)

#RMSE check

ans<- data.frame(answer= all7d$return.pdol, full.lm = predict(full.6, all7d, interval= 'predict'))

RMSE(ans$answer, ans$full.lm.fit)

@@

Feels better. That leaves us with

* inv.mlsto.log
* Discipline
* timespan.cbrt
* no.users
* pc.pro
* Discipline
* Business

RMSE = 0.48266

Going back to full  variables, lets try pairwise multiplying..

```{r, echo=FALSE}
#try diff pairs

pairs.lm<- lm(return.pdol ~ inv.mlsto.log + Discipline + timespan.cbrt + no.users + pc.pro + Business + 
                      inv.mlsto.log*pc.pro + inv.mlsto.log*Business,
              data=all7d)

summary(pairs.lm)
pairs<- predict(pairs.lm, all7d)
ans<- data.frame(answer= all7d$return.pdol, pairs.lm = pairs)

RMSE(ans$answer, ans$pairs.lm)

#down to 0.4759

@@

```{r, echo=FALSE}
#try adding code.client

addone<- function(var= 'JD.Second', df= all7d){
        reduced = df[!(is.na(df[,var])),]
        formula = paste("return.pdol ~ inv.mlsto.log + timespan.cbrt + no.users + Discipline + pc.pro + inv.mlsto.log*pc.pro + inv.mlsto.log*Business", var, sep=" + ")
        add.one = lm(as.formula(formula), data = reduced)

        print(summary(add.one))

        ans= data.frame(answer= reduced$return.pdol, addone.lm = predict(add.one, reduced, interval= 'predict'))

        print(head(ans))

        print(
        paste("RMSE=", RMSE(ans$answer, ans$addone.lm.fit) %>% round(4), sep= " ")
        )

}

#without additional variables, RMSE sits at 0.4759

addone(var='JD.Second', df=all7d)
#RMSE = .4709
addone(var='Post.Code', df=all7d)
#RMSE = .4353
addone(var='majority.pos', df=all7d)
#RMSE = .4541
addone(var='pc.majpos.log', df=all7d)
#RMSE = .4553
addone(var='code.client', df=all7d)
#RMSE = .4394
addone(var='Billing.Type', df=all7d)
#RMSE = .4579
addone(var='code.contact', df=all7d)
#RMSE = .3972

#dont use post code ever. 
#JD.Second doesn't help that much. acutally makes RMSE worse.

@@

Delete Post.Code option

Billing.Type should be paired with inv.mlsto and maybe Discipline

maybe client should be paired with inv.mlsto
maybe JD.Second should be paired with inv.mlsto and code.client and timespan and pc.pro and no.users?? which ever one does something.

majority.pos pair with inv.mlsto
pc.majpos pair with inv.mlsto

Write a function that lists the extra variable you're trying and write out the interaction.

addmult<- function(var= c('JD.Second', 'code.client'), combos= c('JD.Second*inv.mlsto.log'), df= all7d){
        reduced = df[complete.cases(df[,var]),]
        formula = paste("return.pdol ~ inv.mlsto.log + timespan.cbrt + no.users + Discipline + pc.pro + inv.mlsto.log*pc.pro + inv.mlsto.log*Business")

        for(i in 1:length(var)){
                formula = paste(formula, var[i], sep= " + ")
        }

        for(i in 1:length(combos)){
                formula = paste(formula, combos[i], sep= " + ")
        }

        add.one = lm(as.formula(formula), data = reduced)

        print(summary(add.one))

        ans= data.frame(answer= reduced$return.pdol, addone.lm = predict(add.one, reduced, interval= 'predict'))

        print(head(ans))

        print(
        paste("RMSE=", RMSE(ans$answer, ans$addone.lm.fit) %>% round(4), sep= " ")
        )

}

#try Billing.Type with inv.mlsto.log
addmult(var= c('Billing.Type'), combos= c('Billing.Type*inv.mlsto.log'), df= all7d)
# no

#try code.client*inv.mlsto.log
addmult(var= c('code.client'), combos= c('code.client*inv.mlsto.log'), df= all7d)
#made a difference, brought RMSE down to .4076 :)!

#try JD.Second with inv.mlsto.log (no), code.client (too intense), timespan (no), pc.pro (no), no.users (yes)?
addmult(var= c('JD.Second'), combos= c('JD.Second*no.users'), df= all7d)
#add JD.Second*no.users

addmult(var= c('majority.pos'), combos= c('majority.pos*inv.mlsto.log'), df= all7d)
#no

addmult(var= c('pc.majpos.log'), combos= c('pc.majpos.log*inv.mlsto.log'), df= all7d)
#no

It is worthwhile to include:

* code.client by inv.mlsto.log because brought down RMSE from 0.4394 (code.client) to 0.4076 (code.client + code.client by inv.mlsto.log)
* JD.Second by no.users. Brought down RMSE from 0.4709 to 0.4612...

Now look at cross validation for full variable set:

#using caret package
tc <- trainControl("cv",10,savePred=F)
fit<- train(return.pdol ~ inv.mlsto.log + Discipline + timespan.cbrt + no.users + pc.pro + Business + 
                      inv.mlsto.log*pc.pro + inv.mlsto.log*Business,
              data=all7d,
            method = 'lm', trControl = tc)

#RMSE = 0.49246
#compared to non-cross validated
# RMSE = 0.4759

#try using caret package on code.client
fit<- train(return.pdol ~ inv.mlsto.log + Discipline + timespan.cbrt + no.users + pc.pro + Business + 
                      inv.mlsto.log*pc.pro + inv.mlsto.log*Business + code.client,
              data=all7d,
            method = 'lm', trControl = tc)

Not really trying to tune anything via cross validation, however RMSE increased from 0.4759 to 0.49246.

Not THAT bad.

Now, how to get variable importance from lm..

#variable importance for full variables only - pairs.lm
#use varImp from caret package - uses t-test statistic

imp<- varImp(pairs.lm, scale=FALSE)
imp$variable<- rownames(imp)
imp<- imp %>% select(variable, Overall)
imp %>% arrange(-Overall) %>% head()

sum(imp$Overall)

Trial some scenarios:

Run full variables plus

Make a function to output:

* var importances
* RMSE

based on a list of variables that you want to use

sample<- all7d[1000,]
sample<- sample[,!is.na(sample)]
vars<- names(sample) 
vars<- vars[! vars %in% c('mlsto','Year','inv.mlsto','timespan','client.totinv','code.director','Num.disc','Biz.type','Post.Code',
               'code.ProjEng','return.pdol','cost.mlsto','hrs.mlsto','balance.mlsto','client.totinv.log','pc.majpos')]
vars

#make new dataframe for future use with normalised variables and variables that you want to use only
all8a<- all7d %>% select(no.users, Discipline, pc.pro, Business, code.client, JD.Second, timespan.cbrt,
                         inv.mlsto.log,client.totinv.log, pc.majpos.log, code.contact, Billing.Type,
                         majority.pos, return.pdol, mlsto, Year)
write.csv(all8a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all8a.csv')

RMSE<- function(answer, guess, print= TRUE){
        error= answer-guess
        root.error= sqrt(mean(error^2))
        if(print == TRUE){
        print(root.error)
        }
}

final.output<- function(df=all7d, samp = 800) {
        #create sample df
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','inv.mlsto','timespan','client.totinv','code.director','Num.disc',
                                  'Biz.type','Post.Code','code.ProjEng','return.pdol','cost.mlsto','hrs.mlsto',
                                  'dis.sc.mlsto',
                                  'balance.mlsto','client.totinv.log','pc.majpos')]
        variables = vars

        print(
                list("sample case", t(sample %>% select(-Year, -timespan.cbrt, -inv.mlsto.log, -client.totinv.log)))
        )

        #make reduced dataset with complete cases for all variables we want to use
        reduced = df[-samp,]
        reduced = reduced[complete.cases(reduced[,variables]),]

        print(
                paste(nrow(reduced), "cases in full model")
        )

        formula = paste("return.pdol ~ ")

        for(i in 1:length(variables)){
                formula = paste(formula, variables[i], sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'inv.mlsto.log' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*pc.pro', sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'code.client' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*code.client', sep= " + ")
        }

        if('JD.Second' %in% variables &
           'no.users' %in% variables){
                formula = paste(formula, 'JD.Second*no.users', sep= " + ")
        }

        final = aov(as.formula(formula), data = reduced)

        fit= summary(final)

        ans= data.frame(answer= reduced$return.pdol, final.lm = predict(final, reduced, interval= 'predict'))

        # print(head(ans))

        #print variable importances for reduced lm just run

        imp= data.frame('vars'= rownames(fit[[1]]), 'F.val' = fit[[1]]$`F value`)
        #remove white space from levels in imp$vars
        levels(imp$vars)<- sub("\\s+$", "", levels(imp$vars))
        #remove Residuals row
        imp= imp[!(imp$vars %in% 'Residuals'),]

        #print variable importances
        print(
                list("variable importances",
                     imp %>% arrange(-F.val) %>% head())
        )

        #print RMSE for cases that match certain categories only
        #first subset predictions to cases that match the category

        reduced$predict= ans$final.lm.fit

        cats= c('code.client', 'code.contact', 'JD.Second', 'Business', 'no.users', 'majority.pos')

        for(i in 1:length(cats)){
                if(cats[i] %in% vars){
                        cats.red = reduced[reduced[,cats[i]] %in% sample[,cats[i]],]
                        cat.RMSE = RMSE(cats.red$return.pdol, cats.red$predict) %>% round(4)
                        print(
                                paste(cats[i], "RMSE =", cat.RMSE, sep= " "))
                        print(
                                paste("Number of cases =", nrow(cats.red), sep= " "))
                        print(
                                head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto','return.pdol','predict',cats[i])])
                        )
                        }
        }

        num.cats= c('timespan.cbrt', 'inv.mlsto.log', 'pc.pro')

        for(i in 1:length(num.cats)){
                if(num.cats[i] %in% vars){
                        span = 0.05*(max(reduced[,num.cats][i])-min(reduced[,num.cats[i]]))
                        range = c(df[samp,num.cats[i]]-span, 
                                  df[samp,num.cats[i]]+span)
                        cats.red = reduced[reduced[,num.cats[i]]<range[2] & reduced[,num.cats[i]]>range[1],]
                        cat.RMSE = RMSE(cats.red$return.pdol, cats.red$predict) %>% round(4)
                        print(
                                paste(num.cats[i], "RMSE =", cat.RMSE, sep= " "))
                        print(
                                paste("Number of cases =", nrow(cats.red), sep= " "))
                        print(
                                if(num.cats[i] == 'pc.pro'){
                                        head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto','return.pdol','predict',
                                                 num.cats[i])])} 
                                else if(num.cats[i] == 'timespan.cbrt'){
                                                head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto',
                                                                 'return.pdol','predict', 'timespan')])}
                                else {
                                        head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto',
                                                                 'return.pdol','predict')])
                                }

                        )}
        }

        #random RMSE
        r= mean(reduced$return.pdol)
        random.RMSE= RMSE(reduced$return.pdol, r, print=T) %>% round(3)

        print(
        paste("Random Guess RMSE=", random.RMSE , sep= " ")
        )

        #final RMSE for all rows in reduced in a regression
        final.RMSE= RMSE(ans$answer, ans$final.lm.fit) %>% round(3)

        print(
        paste("Overall predicted RMSE=", final.RMSE , sep= " ")
        )

        predict.rpdol = predict(final, sample) %>% round(3)
        predict.rpdol = predict.rpdol[[1]]
        predict.cost = sample$inv.mlsto/(1+predict.rpdol) %>% round(1)
        print(
               paste("return per dollar prediction", predict.rpdol, sep = " ")
        )

        print(
               paste("answer", sample$return.pdol %>% round(3), sep = " ")
        )

        print(
                paste("Invoiced= $", sample$inv.mlsto %>% round(2), ",   predicted cost= $", predict.cost %>% round(1), sep="")
        )

        print(
                paste("Actual cost= $", sample$cost.mlsto %>% round(2), sep="")
        )

}

final.output(df=all7d, samp = 800)

new analysis for thesis write up - include cross validation and delete all the printing

sample<- all7d[1000,]
sample<- sample[,!is.na(sample)]
vars<- names(sample) 
vars<- vars[! vars %in% c('mlsto','Year','inv.mlsto','timespan','client.totinv','code.director','Num.disc','Biz.type','Post.Code',
               'code.ProjEng','return.pdol','cost.mlsto','hrs.mlsto','balance.mlsto','client.totinv.log','pc.majpos')]
vars

#make new dataframe for future use with normalised variables and variables that you want to use only
all8a<- all7d %>% select(no.users, Discipline, pc.pro, Business, code.client, JD.Second, timespan.cbrt,
                         inv.mlsto.log,client.totinv.log, pc.majpos.log, code.contact, Billing.Type,
                         majority.pos, return.pdol, mlsto, Year)
write.csv(all8a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all8a.csv')

RMSE<- function(answer, guess){
        error= answer-guess
        root.error= sqrt(mean(error^2))
        return(root.error)
}

final.output<- function(df=all8a, no.tests = 50, core = TRUE) {

        summary.tests = matrix(NA, nrow = no.tests, ncol = 3)

        for(i in 1:no.tests){

        if(core == FALSE){
        samp = sample.int(nrow(df), 1)                        
        #create sample df - use all variables that are complete from a sample row of data
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','return.pdol')]
        variables = vars
        } else{
                variables = c('inv.mlsto.log', 'Discipline', 'timespan.cbrt',
                              'no.users', 'pc.pro', 'Business')
        }

        #make reduced dataset with complete cases for all variables we want to use
        reduced = df[complete.cases(df[,variables]),]

        formula = paste("return.pdol ~ ")

        for(j in 1:length(variables)){
                formula = paste(formula, variables[j], sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'pc.pro' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*pc.pro', sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'code.client' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*code.client', sep= " + ")
        }

        if('JD.Second' %in% variables &
           'no.users' %in% variables){
                formula = paste(formula, 'JD.Second*no.users', sep= " + ")
        }

        samp_size = floor(0.75*nrow(reduced))
        create.train = base::sample.int(nrow(reduced), samp_size)
        train.df = reduced[create.train,]
        test.df = reduced[-create.train,]

        cats = c('code.client', 'code.contact', 'JD.Second', 'Business', 'majority.pos')
        for(k in seq_along(cats)){
                if(cats[k] %in% vars){
                test.df = test.df[test.df[,cats[k]] %in% unique(train.df[,cats[k]]),]
        }
        }

        final = aov(as.formula(formula), data = train.df)

        fit= summary(final)

        ans = data.frame(answer= test.df$return.pdol, final.lm = predict(final, test.df))

        #print RMSE for cases that match certain categories only
        #first subset predictions to cases that match the category

        test.df$predict= ans$final.lm

        #random RMSE
        r= mean(reduced$return.pdol)
        random.RMSE= RMSE(reduced$return.pdol, r) %>% round(3)

        #final RMSE for all rows in reduced in a regression
        final.RMSE= RMSE(ans$answer, ans$final.lm) %>% round(3)

        summary.tests[i,1]= random.RMSE
        summary.tests[i,2]= final.RMSE
        summary.tests[i,3]= nrow(test.df)
        }
        summary.tests = as.data.frame(summary.tests)
        names(summary.tests) = c('random.RMSE', 'final.RMSE', 'test.nrow')
        return(summary.tests)
}

#how many tests required? power calculation
d.calc = mean(results.core$diff)/sd(results.core$diff)
pwr.t.test(n = NULL, d = d.calc , sig.level = 0.05, power = .8, type = c("one.sample"), alternative = 'greater')
# 3 tests required for results.core

results = final.output(df=all8a, no.tests = 100, core = FALSE)
results = results %>% mutate(diff = random.RMSE - final.RMSE)
results = results %>% filter(diff>-25)
results.core = final.output(df=all8a, no.tests = 50, core = TRUE)
results.core = results.core %>% mutate(diff = random.RMSE - final.RMSE)
saveRDS(results, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/reg_lm.rds")
saveRDS(results.core, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/reg_lm_core.rds")

results %>% ggplot(., aes(x = test.nrow, y = final.RMSE)) + geom_point()

#histogram of difference
results %>% ggplot(., aes(x =diff)) + geom_histogram()

# t- test
t_test = t.test(results$diff, alternative = "greater", mu = 0)
str(t_test)
t_test$p.value

Check what RMSE would be for random guess

```{r, echo=F}

m<- mean(all7d$return.pdol)

RMSE(all7d$return.pdol, m, print=T)

RMSE from random guess is 53 cents.

# delete any code.client or contact. client which has less than 3 entries!
# need to revisit how i got my inv.mlsto, balance.mlsto, cost.mlsto for job 2013.301.2

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')

@@

```{r echo=FALSE}
some <- all7d %>% select(return.pdol, mlsto, inv.mlsto, timespan,no.users,Discipline,pc.pro,
                         client.totinv,code.director,Num.disc,Business,Biz.type,
                         code.contact,code.client,Project.Value,JD.Second,Post.Code,code.ProjEng,Billing.Type,majority.pos,
                         pc.majpos)

@@

RMSE(ans$answer, ans$full.lm)

@@

RMSE is 0.53 which isn't great in terms of predicting return per dollar.
R^2 is 0.2152

```{r, echo=FALSE}
#non full variables
#Post.Code
PostCode<- lm(return.pdol.cbrt ~ Post.Code, data=all7d)
summary(PostCode)
plot(Post.Code ~ return.pdol.cbrt, data=all7d)
abline(PostCode)

#write function

col.lm<- function(vars= 'Post.Code', df=all7d, ret= 'return.pdol.cbrt'){
        #loop through and create lm model's
        names= NULL

        for(i in 1:length(vars)){
                formula = paste(ret, "~", vars[i], sep = " ")
                linear = lm(as.formula(formula), data = df)
                assign(paste(vars[i],"lm",sep="."), linear, envir=.GlobalEnv)

                names = rbind(names, paste(vars[i],"lm",sep="."))

                cat(i," ")
        }

        names = names %>% as.vector
}

#now put all incomplete variables through col.lm function
varis= c('Post.Code', 'majority.pos','pc.majpos.log','code.client', 'JD.Second',
        'Billing.Type','code.contact','Project.Value.log')

lm.vec<- col.lm(vars= varis, df=all7d, ret= 'return.pdol.cbrt')

#compile results of all lm's into ans dataframe

ans.complete<- function(lms = 'Post.Code.lm', df=all7d, ans.df= ans){
        ans.df=ans
        for(i in 1:length(lms)){
                column = predict(get(lms[i]), df)
                #transform from cube root
                column = column^3
                ans.df = cbind(ans.df, column)

                #rename column
                colnames(ans.df)[i+2]<-lms[i]

                cat(i," ")
        }

        ans.df
}

ans.full<- ans.complete(lms=lm.vec, df=all7d, ans.df=ans)

# RMSE(ans$answer, ans$majority.pos.lm) --  doesn't work, need to adjust RMSE function

@@

So now we have our predictions for the full variables as well as a column for each of the incomplete variables.

We want to recombine them using linear regression again!

For a check, I will find all cases which have the full variables as well as client.code, code.contact, and Billing.Type

```{r, echo=FALSE}
#reduce ans data frame to only complete cases with variables you are interested in
ans.red = ans.full %>% select(answer, full.lm, code.client.lm, Billing.Type.lm, code.contact.lm)
ans.red <- ans.red[complete.cases(ans.red),]

#run final lm
final.lm<- lm(answer~. , data=ans.red)
final<- predict(final.lm, ans.red)
ans.red$final.lm<- final

RMSE(ans.red$answer, ans.red$final.lm)

ans.red %>% View

@@

Wouldnt you be better off just running a regression with the complete cases?

reduced<- all7d %>% select(inv.mlsto.log , timespan.cbrt , no.users , Discipline , pc.pro , client.totinv.log , 
                                   code.director , Num.disc , Business , Biz.type , code.ProjEng, Billing.Type,
                           code.client, code.contact, return.pdol.cbrt)
reduced<- reduced[complete.cases(reduced),]

test.lm<- lm(return.pdol.cbrt ~ ., data= reduced)
test<- predict(test.lm, reduced)
ans.red$test.lm <- test

RMSE(ans.red$answer, ans.red$test.lm)

@@

### 2016-12-13 boost_tree.rmd
reset

all9c$b.inv.log <- man.clust(first.vec=all9c$inv.mlsto.log, 
                            breaks.man= log(breaks),
                            labs = c("100-600","600-2.5k","2.5k-8k","8k-60k","60k-1.8m"
                            ))

@@

@@

cv.Control <- trainControl(method = "cv",
                           number = 5,
                           seeds= seeds
                           , summaryFunction=twoClassSummary,
                           classProbs=TRUE
                           )
gbmGrid <- expand.grid(shrinkage = c(0.001),
                       n.trees = c(10000), interaction.depth = c(3,4,5,6),
                       n.minobsinnode = c(20))
set.seed(2)
gbmFit <- train(as.formula(formula), data= train2,
                 method = "gbm", trControl = cv.Control, verbose = FALSE,
                 bag.fraction = 0.5, tuneGrid = gbmGrid,
                metric = 'ROC',
                na.action = na.pass)

>>>>

all9c$b.inv.log <- man.clust(first.vec=all9c$inv.mlsto.log, 
                            breaks.man= log(breaks),
                            labs = c("100-600","600-2.5k","2.5k-8k","8k-60k","60k-1.8m"
                            ))
# all9c <- read.csv('C:/Users/n9232371/OneDrive/shared files/Bligh Tanner/masters/data/all9c.csv')[,-1]

@@

#create test train
sample<- sample(1:nrow(all9c), 3/4*nrow(all9c), replace=F)
train<- all9c[sample,]
test<- all9c[-sample,]

@@

cv.Control <- trainControl(method = "cv",
                           number = 5,
                           seeds= seeds
                           , summaryFunction=twoClassSummary,
                           classProbs=TRUE
                           )
gbmGrid <- expand.grid(shrinkage = c(0.001),
                       n.trees = c(10000), interaction.depth = c(4),
                       n.minobsinnode = c(20))
set.seed(2)
gbmFit <- train(as.formula(formula), data= train2,
                 method = "gbm", trControl = cv.Control, verbose = FALSE,
                 bag.fraction = 0.5, tuneGrid = gbmGrid,
                metric = 'ROC',
                na.action = na.pass)
